# Various Shapes
========================================================

- To create a plot, use the command plot()

```{r, plot, fig.width=7, fig.height=7, message=FALSE }
plot(1:2,xlim=c(0,100), ylim=c(0,100), type="n", xlab="", ylab="")
```

- To create a polygon, use the command polygon()

```{r fig.width=7, fig.height=7}
plot(1:2,xlim=c(0,100), ylim=c(0,100), type="n", xlab="", ylab="")
polygon(c(25,35,35,25),c(25,25,35,35),col="red",border="black")
```

- In order to create a circle, install the poltrix package, and use the command draw.circle()
```{r fig.width=7, fig.height=7}
plot(1:2,xlim=c(0,100), ylim=c(0,100), type="n", xlab="", ylab="")
draw.circle(50,50,20,20,nv=100,border="NA",col="lightblue")
```

- The second polygon is created similarly to the square, except 5 points are plotted because it is a pentagon
```{r fig.width=7, fig.height=7}
plot(1:2,xlim=c(0,100), ylim=c(0,100), type="n", xlab="", ylab="")
polygon(c(58,63,83,88,73),c(85,65,65,85,95),col="yellow",border="NA")
```

- An ellipse can be drawn using the draw.ellipse() command from the plotrix package
```{r fig.width=7, fig.height=7}
plot(1:2,xlim=c(0,100), ylim=c(0,100), type="n", xlab="", ylab="")
draw.ellipse(20,60,10,25,col="lightpink",border="NA")
```

- The last sqaure can be drawn using the polygon() command
```{r fig.width=7, fig.height=7}
plot(1:2,xlim=c(0,100), ylim=c(0,100), type="n", xlab="", ylab="")
polygon(c(15,30,30,15),c(45,45,60,60),col="green",border="blue")
```

- Together on a plot, it looks like this:
```{r fig.width=7, fig.height=7}
plot(1:2,xlim=c(0,100), ylim=c(0,100), type="n", xlab="", ylab="")
polygon(c(25,35,35,25),c(25,25,35,35),col="red",border="black")
draw.circle(50,50,20,20,nv=100,border="NA",col="lightblue")
polygon(c(58,63,83,88,73),c(85,65,65,85,95),col="yellow",border="NA")
draw.ellipse(20,60,10,25,col="lightpink",border="NA")
polygon(c(15,30,30,15),c(45,45,60,60),col="green",border="blue")
```
